---
title: "Figuring out the big ROC curve plots"
output: html_notebook
---


After doing the Cyclone based big runs the different levels of things that
actually have different levels are:

- `scenario`:  WF and nonWF
- `mig_rate1` and `mig_rate2`:  These are identical to one another, with 4 values.
- `samp_ppn`: 4 levels
- var and diag miss rates.  Not parsed perfectly. but 0, 0.15, 0.25, 0.5
- cohort inclusion: 2 levels
- full_sib_treatment: two levels (but also some NA's...)


Note, when method = NA know it is sequoia.

So, for looking at all of these, I think we can do like what we did before,
but look at different sampling ppn and mig_rates on different pages.

That is 16 different pages.  Yowzers.  That will work for a supplement...maybe.

We can do that by nesting stuff up.
```{r}
library(tidyverse)
dir.create("outputs/004", recursive = TRUE, showWarnings = FALSE)

BR <- read_rds("stored-results/BIG-RUN-all-rocs.rds")

nesto <- BR %>%
  group_by(mig_rate1, mig_rate2, samp_ppn) %>%
  nest()

rm(BR)
```


Now, each one of these nested ones we should be able to plot in a consistent way
on a separate page.  Here is a function to do that:
```{r}
roc_page <- function(mig_rate, samp_ppn, x, outfolder = "outputs/004") {

  x2 <- x %>%
    mutate(
      method = replace_na(method, "sequoia"),
      full_sib_treatment = replace_na(full_sib_treatment, "none"),
      miss_rate = var_miss_rate
    ) %>%
    mutate(
      approach = case_when(
        method == "sequoia" ~ "Sequoia (variable only)",
        remainder == "hot_both_diag_and_var_rocs.rds" ~ "HOT (diagnostic + variable)",
        remainder == "hot_only_var_rocs.rds" ~ "HOT (variable only)",
        method == "mup" & full_sib_treatment == "discarded_likely_FS" ~ "MixedUpParents (w/FS-calc)",
        method == "mup" & full_sib_treatment == "none" ~ "MixedUpParents (no FS-calc)",
        TRUE ~ NA_character_
      )
    )
  
  
  g <- x2 %>%
    ggplot(aes(x = fpr, y = tpr, colour = approach, group = interaction(approach, rep))) +
    facet_grid(miss_rate ~ scenario + cohort_inclusion) +
    geom_line() +
    scale_colour_brewer(type = "qual", palette = "Set1") +
    ggtitle(str_c("Migration Rate: ", mig_rate, "   Sampled Fract: ", samp_ppn))
  
  outpath <- str_c(outfolder, "/mig-rate_", mig_rate, "--samp-fract_", samp_ppn, ".pdf")
  
  ggsave(
    g, 
    filename = outpath, 
    width = 15, height = 15
  )
  
  outpath
  
}
```
And now, we can use it like this:
```{r}
BOING <- nesto %>% 
  mutate(
    plot = pmap_chr(
      .l = list(mig_rate = mig_rate1, samp_ppn = samp_ppn, x = data),
      .f = roc_page,
      .progress = TRUE
    )
  )
```


That is cool.  Now, let's crunch out the small-pop (120) runs.

