---
title: "Getting Pictures of the Admixture"
output: html_notebook
---

From out main simulations, I want to make pictures of the admixture fractions for
some representative cases.  But I don't want to write a rule to do this, so I will
just implement it by hand on the cluster after having done the one big run.

First off, find the files on the cluster like this:
```r
files <- Sys.glob("results/scenario-cyclone*/*/rep-1/slim-output.rds")

names(files) <- files

AllRep1 <- lapply(files, function(x) {
  tmp <- read_rds(x)
  tmp$true_segs %>% 
    filter(ind_time == 0) %>%
    group_by(ind_pop, ind_time, ind_id, trit) %>%
    summarise(tot = sum(right - left))
}) %>%
  bind_rows(.id = "path")
  
write_rds(AllRep1, file = "stored-results/TrueSegSummary-BigRun-Rep1s.rds", compress="xz")
```

And then I copied that to stored_results on my laptop.

Then we can read it and make some plots:
```{r}
library(tidyverse)

dir.create("outputs/005", recursive = TRUE, showWarnings = FALSE)
dat <- read_rds("stored-results/TrueSegSummary-BigRun-Rep1s.rds") %>%
  extract(
    path,
    into = c("scenario", "mig_rate"),
    regex = "results/scenario-(.+)/ps1-1200-ps2-1200-mr1-([0-9.]+)-mr"
  )
```

Now, we want to sort each fish in its own group by admixture fraction.
```{r}
ranks <- dat %>%
  group_by(scenario, mig_rate, ind_pop, ind_id) %>%
  summarise(AdmixA = sum( (trit == 2) * 2 * tot + (trit == 4) * tot) / (2 * sum(tot))) %>%
  arrange(scenario, mig_rate, ind_pop, desc(AdmixA)) %>%
  mutate(rank = 1:n())


dat2 <- dat %>%
  left_join(ranks, by = join_by(scenario, mig_rate, ind_pop, ind_id)) %>%
  ungroup() %>%
  mutate(
    Ancestry = case_match(
      trit,
      2 ~ "AA",
      4 ~ "AB",
      6 ~ "BB",
      .default = NA
    )
  ) %>%
  group_by(scenario, mig_rate,ind_pop, ind_id) %>%
  mutate(
    Fraction = tot / sum(tot)
  ) %>%
  ungroup() %>%
  mutate(
    scenario = case_match(
      scenario,
      "cyclone_nonWF" ~ "non-Wright-Fisher",
      "cyclone_WF" ~ "Wright-Fisher"
    ),
    ind_pop = case_match(
      ind_pop,
      1 ~ "Pop 1",
      2 ~ "Pop 2"
    )
  ) 

  
```


Now we should be able to make some plots:
```{r}
g <- ggplot(dat2, aes(x = rank, y = Fraction, fill = Ancestry)) +
  geom_col() +
  facet_grid(mig_rate ~ scenario + ind_pop, scales = "free_x") +
  theme_bw() +
  xlab("Individuals arranged according to admixture fraction") +
  scale_fill_manual(values = c(AA = "#d7191c", AB = "#fdae61", BB = "#2c7bb6"))


ggsave(g, filename = "outputs/005/ancestry-fracts-of-sims.pdf", width = 10, height = 12)

g
```
