---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# MixedUpParents-sims-and-analyses

The full workflow runs the large simulation studies presented in the paper
"MixedUpParents: A New and Improved Method for Genetic Parentage1
Assignment in Admixed Populations."
For a smaller reproducibility check, the Snakefile includes a `README_example`
rule.  It requests four ROC-curve outputs from replicate 2 of one
`cyclone_nonWF` scenario:

- `naive_logl_both_diag_and_var_rocs.rds`
- `mup_rocs.rds`
- `hot_both_diag_and_var_rocs.rds`
- `relate_admix_both_diag_and_var_rocs.rds`

Run a dry-run of that example with:

```sh
snakemake -np --use-conda  --cores 8 \
  README_example \
  --config mup_conda="$HOME/miniforge3/envs/mixed-up-parents"
```

Remove `-n` to actually run the example, which will take about 30 minutes on
a typical laptop.  

The `mup_conda` config value should
point to the conda environment used by `MixedUpSlimSims`/`MixedUpParents`; the
workflow exports it as `MUP_CONDA` for `reticulate`.

The RelateAdmix part of the example also expects `plink`, `admixture`, and
`relateAdmix` to be available on `PATH`. Those dependencies are not handled
via conda.

The MUP log-likelihood rule uses
Snakemake's `--use-conda` machinery to create the small bedtools environment in
`envs/bedtools.yaml`.

## Plotting Tools

The ROC figures appearing in the paper were made from the gathered parentage ROC
curves produced by rule `gather_rocs` in the notebooks `004-ROCs-for-big-runs.Rmd`
for the full-scale runs and `004.1--ROCs-for-the-small-120-runs.Rmd` for the smaller
set of runs with a higher chance of Sequoia finishing in less than 24 hours.  

The run time boxplots in the paper were created within the notebook
`007-harvest-and-present-benchmarks.Rmd` using Snakemake's benchmark outputs
for each rule invocation.

Note that a separate branch of this repo (`rerun-sequoia-smalls`) was maintained for running
the small-sample cases, and another (`relate-admix-on-alpine`) was used to run RelateAdmix
on the Alpine cluster.  

## Notes re: Running on the SEDNA Cluster
 
Something weird goes on with SEDNA whereby the slim_sim rule writes all its output
no problem, and then fails when returning control back to Snakemake.  It might
have something to do with the reticulate package and its conda environment.

At any rate, you can run it like this (which is assuming that we are running snakemake
on a node with 10 cores, 9 of which we will use for local jobs):
```sh
snakemake -np --use-envmodules --keep-incomplete --until slim_sim --profile hpcc-profiles/slurm/sedna
```
and once that is done, the outputs will still be there and you can continue by simply
removing the `.snakemake/incomplete` directory and then doing:
```sh
snakemake -np --use-envmodules --use-conda --local-cores 19 --profile hpcc-profiles/slurm/sedna
```

Total PITA.  Gonna have to figure out why it is failing, but we can use the above
until that time.

We might be able to use --cleanup-metadata 

Note, the --use-conda on the second line is to have bedtools for mup_logls.

You also need to pass the `mup_conda` config value, as in the README example
above.






## Notes on scenarios:

**Langford simulations**

Migration rates: symmetrical at 0, 2, 5, and 10%
Missing indiv rate: 0, 25, 50, 75%
Missing locus rate: 0, 0.15, 0.25, 0.5

5 reps of each.

Don't bother with Sequoia for the same cohort included runs, none of them
finished!

Calculate number of markers shared for each pair.


**Sequoia Runs with smaller sample sizes**

I am making a separate config for these.  I am going to do:

- sampling fract = 0.5
- missing genotype rate = 0.25 or 0.5
- all migration rates
- pop sizes of 120

I hope that will finish.  This is all specified in a separate config called
`config/config_120.yaml`.

**Other cases**

Fst = 0, hack things up so that we can tease out how much performace is due to SOS
model vs better-estimated allele freqs.


## Making a sim-spec.csv file

This is just some example code on how to make these
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
sim_specs <- expand_grid(
  sim_scenario = c("cyclone_WF", "cyclone_nonWF"),
  num_reps = 5,
  pop_size_1 = 1200,
  pop_size_2 = 1200,
  nesting(
    mig_rate_1 = c(0.0, 0.02, 0.05, 0.1),
    mig_rate_2 = c(0.0, 0.02, 0.05, 0.1),
  ),
  prop_sampled = c(1.0, 0.75, 0.5, 0.25),
  err_var = 0.01,
  err_diag = 0.004,
  nesting(
    miss_var = c(0, 0.15, 0.25, 0.5),
    miss_diag = c(0, 0.15, 0.25, 0.5),
  )
)
```

Only do certain Sequoia runs.  Based on previous runs the only ones that will finish
in a reasonable amount of time appear to be:

- exclude_same_cohort
- var only
- missing locus proportion of 0, 0.15

# Making the small (120 indivs) simulations

```{r}
library(tidyverse)
sim_specs <- expand_grid(
  sim_scenario = c("small_cyclone_WF", "small_cyclone_nonWF"),
  num_reps = 5,
  pop_size_1 = 120,
  pop_size_2 = 120,
  nesting(
    mig_rate_1 = c(0.0, 0.02, 0.05, 0.1),
    mig_rate_2 = c(0.0, 0.02, 0.05, 0.1),
  ),
  prop_sampled = c(0.5),
  err_var = 0.01,
  err_diag = 0.004,
  nesting(
    miss_var = c(0.25, 0.5),
    miss_diag = c(0.25, 0.5),
  )
)
```

Even at that, with full sampling of individuals we might have some really long ones. But at least that will give us only  2 * 5 * 4 * 4 * 2 = 320 runs of sequoia, and they should be shorter

I will modify the aggregation functions to have an option to do only those.

I did that, and I was able to run it with:
```sh
snakemake -np --use-envmodules --use-conda --local-cores 3  --configfile config/config_120.yaml  --profile hpcc-profiles/slurm/sedna
```
5 of the sequoia runs had not finished in 48 hours.  So I just removed them from the
targets.  Those files are in 
```
config/black-lists/sequoia-short-run-timeouts.txt
```


